\documentclass{beamer}
\title{Parallel Processing in Go}
\subtitle{Flyfishing and a Monte Carlo Experiment}
\author{Matt Belisle}
\date{BigSky DevCon 2013-06-21}
\begin{document}
\frame{\titlepage}
\begin{frame}
  \frametitle{What is Go?}

  Go is an open source programming language which began development in
  2007.  It is ...
  
  \begin{itemize}
    \item Compiled
    \item Garbage collected
    \item Type/memory safe
    \item Concurrent
    \item Namespaced
    \item OOP friendly
    \item Unicode based
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Who made Go?}

  Google hired a few old time pioneers to design and develop Go.
  
  \begin{itemize}
    \item Ken Thompson (C and Unix)
    \item Rob Pike (Unix and UTF-8)
    \item Robert Griesemer (not as famous)
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{What are the goals?}

  Go aims to be ...
  
  \begin{itemize}
    \item Intuitive to learn
    \item Quick to develop
    \item Blazing fast
    \item Beautifully parallel
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Can we see some Go?}
  \framesubtitle{And what about flyfishing?}
  \begin{center}
    \url{https://github.com/mgbelisle/flyfishing}
  \end{center}
\end{frame}
\begin{frame}
  \frametitle{Should your project be written in Go?}
  Go is a bad language to choose if ...
  \begin{itemize}
    \item Your app needs a UI toolkit
    \item The devs need mountains of example code
  \end{itemize}
  \bigskip
  Go is a good language to choose if ...
  \begin{itemize}
    \item Your app needs to do lots of things at the same time
    \item Your app needs to be fast
    \item Your infrastructure needs to be distributed/scalable
    \item The devs embrace the ``Zen of Python''
  \end{itemize}
\end{frame}
\end{document}